---
title: "Cars.com (part 1)"
author: "XX NAMES HERE"
date: "2025-02-XX"
date-format: iso
format: pdf
toc: true
editor: source
---

```{r}
#| label: setup
#| include: false
library(mosaic)   
library(tidyverse)
options(scipen = 5)
```

This assignment is due by the end of the day on Thursday, February 27th.
Please submit as a group assignment on Moodle (including your partner).

We collected prices on n = XX used Toyota Prius's from cars.com within a XX mile radius of XX (zip code YY).

### STEP 1: Summarize/check what you entered

SOLUTION:

```{r}
#| message: false
# be sure to upload cars.csv to RStudio in the same folder as this file
ds <- read_csv("cars.csv")
ds <- ds |>
  mutate(
    year_char = as.character(year)
  )
glimpse(ds)
```

```{r}
# some summary statistics (please delete those that you are not using)
tally(~ car, data = ds)
tally(~ model, data = ds)
tally(~ year, data = ds)
tally(~ location, data = ds)
df_stats(~ price, data = ds)
df_stats(~ mileage, data = ds)
```

SOLUTION: 

XX summary of distribution of variable 1 XX

XX summary of distribution of variable 2 XX

\newpage

### STEP 3: Generating an interestimg plot with at least three variables

```{r}
#| warning: false
# here are some of my ideas: please explore and elaborate using some different plots
# be sure to remove these examples
gf_boxplot(price ~ year_char, data = ds)
gf_boxplot(mileage ~ year_char, data = ds)
gf_point(price ~ mileage, data = ds) |> 
  gf_lm() |>
  gf_smooth(se = FALSE)
gf_point(price ~ year, data = ds) |> 
  gf_lm() |>
  gf_smooth(se = FALSE)
```

SOLUTION:

```{r}
# your new plot goes here

```

XX HERE IS OUR INTERESTIMG PLOT

\newpage


### STEP 4: Fit and interpret a multiple regression model


```{r}
# here's my example (with just one predictor)
lm1 <- lm(price ~ year, data = ds)
coef(lm1)
# your model should have at least two predictors!
```

SOLUTION: 

XX OUR INTERPRETATION HERE XX


